\TitleFont Characterization of reconstruction error in compressively sampled speech

### 2020-02-11 main.tex
add intro

\documentclass[10pt,a4paper,twoside]{article}
\input{spp.dat}

@@

\title{\TitleFont Compressive Sensing: Applications from 1-D to $N$-D}

@@

\keywords{compressive sensing, sub-Nyquist sampling, signal processing}

@@

\section{Introduction}\label{sec:intro}

\begin{figure}[tb]
\centering
\includegraphics[width=0.3\linewidth]{figure1.pdf}
\caption{This is an example of a single column-wide figure. Figure captions are preferably self-contained and in vector format (versus raster format).}
\label{fig:plot1}
\end{figure}

\begin{figure}[tbp]
  \centering
  \subfloat[Optional subcaption of this subfigure.]{\makebox[0.4\textwidth]{{\includegraphics[width=0.2\textwidth]{figure1.pdf}\label{fig:f1}}}}
  \quad % or other spacing between figures
  \subfloat{\makebox[0.4\textwidth]{\includegraphics[width=0.3\textwidth]{figure2.jpg}\label{fig:f2}}}
  \caption{Multiple images can be inserted inline.}\label{fig:plots}
\end{figure}

\begin{table}[b]
\centering % center-align tables within a column
\caption{This is an example of a single column table. Captions are preferably self-contained and placed above the table. Columns may be left-, center-, decimal marker-, or right-aligned.}\label{table:label1}
\begin{tabular}{l c d{2.3} r}
\toprule
Example & Count 	1			& \multicolumn{1}{c}{Count 2} & Total\\
\midrule
A 						& 2.345 					& 5.435 																		& 16.78(3)\\
B 						& 3.0 							& 12.0																				& 43.2(5)\\
\bottomrule
\end{tabular}
\end{table}

@@

>>>>

\documentclass[10pt,a4paper,twoside]{article}
\input{spp.dat}
\usepackage{physics}
\usepackage{amsfonts}
\usepackage{graphicx}
\graphicspath{{images/}}

@@

\title{\TitleFont Characterization of reconstruction error in compressively sampled speech}

@@

\keywords{compressive sensing, signal processing, compressive speech enhancement}

@@

\section{Introduction}\label{sec:intro}
Conventional sensing devices are based on the Nyquist-Shannon sampling theorem (NST), which states that given a signal's bandwidth, one can capture all the pertinent information about that signal if it is sampled at a rate

\begin{equation} \label{eq:nst}
	f_S \geq 2f_B
\end{equation}

\noindent where $f_B$ is the signal's highest frequency component, and $2f_B$ is known as the Nyquist rate \cite{Shannon1949}. After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some domain. For regular consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works flawlessly. However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful \cite{Candes2008b}. Cand\'{e}s et al. \cite{Candes2006} and Donoho et al. \cite{Donoho2006} independently pioneered compressive sensing (CS), which could directly sample the portions of a signal that would otherwise survive the compression stage in conventional sampling. In this new sampling paradigm, we consider the linear model of signal acquisition

\begin{equation}\label{eq:cesa}
	\vec{y} = \vec{A}\vec{x} \equiv \innerproduct{\vec{x}}{\vec{a}_k}
\end{equation}

In other words, the signal vector $\vec{x} \in \mathbb{R}^n$ is correlated with the basis waveforms $\vec{a}_k$ to yield a compressed information vector $\vec{y} \in \mathbb{R}^m$, where $m \ll n$. This causes the task of recovering $\vec{x}$ from $\vec{y}$ impossible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}. This can be circumvented by enforcing constraints based on models of natural signals, as well as those based on optimization techniques. In particular, reconstruction can be achieved by enforcing sparsity and incoherence constraints \cite{Candes2008b}. From this, the process of reconstruction is then recast into a general minimization problem

\begin{equation}\label{eq:minl1}
	\min_{\vec{x}} \norm{\vec{x}}_1 \quad \textrm{subject to} \quad \vec{A}\vec{x} = \vec{y}
\end{equation}

\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=\textwidth]{clean-pesq-snr.png}
	\caption{Two most commonly used metrics in evaluating quality of reconstructed speech recordings. PESQ is sensitive to the signal compression (left), while the average segmental SNR is sensitive to the number of subbands (right).}
	\label{fig:pesq-snr}
\end{figure}
